---
title: Behavior Analysis
author: Liang Zhang
date: 2022-11-17
format: 
  revealjs:
    code-fold: false
execute: 
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
targets::tar_load(indices_clean)
targets::tar_load(indices_wider)
targets::tar_load(indices_wider_clean)
targets::tar_load(mdl_data)
```

# Data Inspection

## Distributions

```{r}
#| label: fig-distr
#| fig-width: 8
#| fig-height: 6
#| fig-cap: >
#|   **Distributions for All Tasks.** They are all all fairly distributed as 
#|   normal.
indices_clean |> 
  ggplot(aes(score)) +
  geom_histogram() +
  facet_wrap(~ disp_name + index, scales = "free")
```

## Missing Pattern

```{r}
#| label: fig-miss-pattern
#| fig-width: 8
#| fig-height: 6
#| fig-cap: >
#|   **Misssing pattern.** Stop signal task has slightly more missing values.
#|   Subjects with missing values at more than 20% of tasks are removed in
#|   further analysis.
indices_wider |> 
  select(-sub_id) |> 
  naniar::vis_miss() +
  theme(axis.text.x = element_text(angle = 90))
```

# Model Building

## Correlation Matrix

```{r}
#| label: fig-correlation
#| fig-width: 8
#| fig-height: 8
#| fig-cap: "**Correlation Between Tasks**"
mdl_data |> 
  corrr::correlate() |> 
  corrr::autoplot()
```

## The promising models

:::: {.columns}

::: {.column}
```{r}
#| label: fig-common-fac
#| fig-width: 8
#| fig-height: 8
#| fig-cap: "**Common Factor Model**"
fit <- psych::fa(mdl_data, 5)
psych::fa.diagram(fit)
```
:::

::: {.column}
```{r}
#| label: fig-bifac
#| fig-width: 8
#| fig-height: 8
#| fig-cap: "**Bi-Factor Model**"
fit <- psych::omega(mdl_data, 5, plot = FALSE)
psych::omega.diagram(fit)
```
:::

:::

## Further Thoughts

Some critical issues:

* Models with one latent factor only have poor model fitting.
  - Workaround: using bi-factor model and estimate general factor from the `g` factor.
* Subjects with missing values can be hard to estimate factor scores
  - Workaround: using CFA and full-information maximal likelihood method.
