---
title: Behavior Analysis
author: Liang Zhang
date: 2022-11-17
format: 
  revealjs:
    code-fold: false
execute: 
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
targets::tar_load(indices)
indices_clean <- indices |> 
  group_by(disp_name) |> 
  filter(!performance::check_outliers(score, method = "iqr")) |> 
  ungroup()
indices_wider <- indices_clean |> 
  unite("task_index", disp_name, index, remove = FALSE) |> 
  pivot_wider(
    id_cols = sub_id,
    names_from = disp_name,
    values_from = score
  )
```

# Data Inspection

## Distributions

```{r}
#| label: fig-distr
#| fig-width: 8
#| fig-height: 6
#| fig-cap: >
#|   **Distributions for All Tasks.** They are all all fairly distributed as 
#|   normal.
indices_clean |> 
  ggplot(aes(score)) +
  geom_histogram() +
  facet_wrap(~ disp_name, scales = "free")
```

## Missing Pattern

```{r}
#| label: fig-miss-pattern
#| fig-width: 8
#| fig-height: 6
#| fig-cap: >
#|   **Misssing pattern.** Stop signal task has slightly more missing values.
#|   Subjects with missing values at more than 20% of tasks are removed in
#|   further analysis.
indices_wider |> 
  select(-sub_id) |> 
  naniar::vis_miss() +
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
#| label: rm-sub-too-much-miss

# use {tidytable} locally, which is faster
indices_wider_clean <- withr::with_package(
  "tidytable",
  indices_wider |> 
    rowwise() |> 
    # mutate(prop_miss = mean(is.na(c_across(-sub_id)))) |> 
    filter(mean(is.na(c_across(-sub_id))) < 0.2) |>
    ungroup()
)
mdl_data <- select(indices_wider_clean, -sub_id)
```

# Model Building

## Correlation Matrix

```{r}
#| label: fig-correlation
#| fig-width: 8
#| fig-height: 8
#| fig-cap: "**Correlation Between Tasks**"
mdl_data |> 
  corrr::correlate() |> 
  corrr::autoplot()
```

## The promising models

:::: {.columns}

::: {.column}
```{r}
#| label: fig-common-fac
#| fig-width: 8
#| fig-height: 8
#| fig-cap: "**Common Factor Model**"
fit <- psych::fa(mdl_data, 4)
psych::fa.diagram(fit)
```
:::

::: {.column}
```{r}
#| label: fig-bifac
#| fig-width: 8
#| fig-height: 8
#| fig-cap: "**Bi-Factor Model**"
fit <- psych::omega(mdl_data, 4)
psych::omega.diagram(fit)
```
:::

:::

## Further Thoughts

Some critical issues:

* Models with one latent factor only have poor model fitting.
  - Workaround: using bi-factor model and estimate general factor from the `g` factor.
* Subjects with missing values can be hard to estimate factor scores
  - Workaround: using CFA and full-information maximal likelihood method.
